---
title: "Code (PostgreSQL)"
output: html_document
author: Zoé Wolter
date: "2023-08-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data

```{r}
eurostat <- readxl::read_excel(here::here('data/eurostat-data.xlsx'), 
                               sheet = "Sheet 1", skip = 12)
```

## Preprocessing 

Before the data is stored in the database for further processing, some initial preprocessing has to be done due to the Excel format of the original data:
```{r}
# define not in operator
`%notin%` <- Negate(`%in%`)

# cleaning
eurostat <- eurostat %>%
  dplyr::select(
    nuts2 = TIME...1,
    region = TIME...2,
    year2019 = `2019`,
    comment2019 = ...4,
    year2020 = `2020`,
    comment2020 = ...6,
    year2021 = `2021`,
    comment2021 = ...8,
    year2022 = `2022`,
    comment2022 = ...10,
  ) %>%
  dplyr::filter(
    nuts2 %notin% c('GEO (Codes)', 'EU27_2020', 'EA20', NA, 'Special value',
                    ':', 'Available flags:', 'du', 'bd', 'bu', 'b', 'd', 'bdu', 'u')
  )

# check variable classes
purrr::map(eurostat, class)
```

## Database Setup

Create and connect to database `dataproject`:
```{r}
# connect to postgres 
db <- dbConnect(Postgres(),
                user = "correlaid", 
                password = "")

db <- dbConnect(Postgres(),
                user = "dpuser", 
                password = "dppassword")

# create database if it does not exist yet
dbExecute(db, "CREATE DATABASE dataproject;")

# connect to database
db <- dbConnect(Postgres(),
                dbname = "dataproject",
                user = "correlaid", 
                password = "")

db <- dbConnect(Postgres(),
                dbname = "dataproject",
                user = "dpuser", 
                password = "dppassword")
```

Write dataset `eurostat` to database:
```{r}
# if the table 'eurostat' already exists in the database, then first remove it
# dbExecute(db, 'DROP TABLE eurostat')

# write dataset to database
dbWriteTable(db, 'eurostat', eurostat)

# check
dbListTables(db) 
dbGetQuery(db,
           'SELECT nuts2
            FROM eurostat
            LIMIT 5;')
```

## Data Processing

Drop variables which are not relevant for the further analysis. As the last EP election was in 2019, the data on employment status of persons with foreign citizenship in this year is selected:
```{r}
# drop irrelevant variables 
dbExecute(db,
          'ALTER TABLE eurostat
           DROP COLUMN comment2019,
           DROP COLUMN year2020,
           DROP COLUMN comment2020,
           DROP COLUMN year2021,
           DROP COLUMN comment2021,
           DROP COLUMN year2022,
           DROP COLUMN comment2022;')

# check
dbGetQuery(db,
           'SELECT *
            FROM eurostat
            LIMIT 5;')

# recode NA's
dbExecute(db,
          "UPDATE eurostat
           SET year2019 = NULL
           WHERE year2019 = ':';")

# check
dbGetQuery(db,
           'SELECT * 
            FROM eurostat 
            WHERE year2019 IS NULL;')

# check datatypes
dbGetQuery(db,
           "SELECT *
            FROM INFORMATION_SCHEMA.COLUMNS 
            WHERE TABLE_NAME = 'eurostat';")

# convert text to number for employment rate
dbExecute(db,
          "ALTER TABLE eurostat
           ADD emp2019 real;")

dbExecute(db,
          "UPDATE eurostat
           SET emp2019 = CAST(year2019 AS real)")

# check and drop unnecessary column
dbGetQuery(db,
           "SELECT emp2019, CAST(year2019 AS real) 
           FROM eurostat;")
dbExecute(db,
          'ALTER TABLE eurostat
           DROP COLUMN year2019;')
```

## Data Analysis

Average of employment rates for persons with foreign citizenship over all regions:
```{r}
dbGetQuery(db,
           'SELECT avg(emp2019)
            FROM eurostat;')
```

Regions with the lowest employment rate of persons with foreign citizenship:
```{r}
dbGetQuery(db,
           'SELECT *
            FROM eurostat
            ORDER BY emp2019
            LIMIT 10;')
```

Regions with the lowest employment rate of persons with foreign citizenship:
```{r}
dbGetQuery(db,
           'SELECT *
            FROM eurostat
            WHERE emp2019 IS NOT NULL
            ORDER BY emp2019 DESC
            LIMIT 10;')
```

## Export Table 

Store table as csv to be merged with other data table:
```{r}
eurostat <- dbGetQuery(db,
                       'SELECT *
                       FROM eurostat;')

readr::write_csv(x = eurostat,
                 file = here::here('data/eurostat-processed.csv'))
```


## Disconnect from Database

```{r}
dbDisconnect(db)
```

